### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

@@

>>>>

\subsection{Measuring the time}

@@

\subsection{GLPK: native vs. Cygwin}

In this experiment we will try to remove one of the variables out of the equation: that is the effect of different versions of GLPK on the overall results. The rationale is this: on Windows systems, the two most accessible ways to install GLPK are via a binary distribution TODO link, or via Cygwin as one of its packages.

If we find out which of these Cygwin version is better, we will be using it exclusively without very much fear that this could affect any other aspect of our experiments. We might also find that there is no relevant difference, which would be good, too.

\begin{table}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine & Windows \\
  Input data set & \texttt{100-500} \\
  Iterations & 20 \\
  \hline
  \end{tabular}
\end{table}
